The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-10-12 paper/paper.Rmd
denonymize

---
title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
link-citations: true
authors:
  - name: Person One
    email: personone@domain.com
  - name: Person Two
    email: persontwo@domain.com
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence supporting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine the proportion of round wins immediately following a win streak. Given the round index, streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Finally, we find that sequences of round wins that are identified as non-random by the Wald-Wolfowitz run tests do not occur more or less frequently than expectated, further failing to provide evidence for the hot hand effect.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---

@@

[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/author/repo/blob/master/data/file.csv>.

>>>>

---
title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
link-citations: true
authors:
  - name: Tony ElHabr
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
  - name: Andrew ElHabr
    email: andrewelhabr@gatech.edu
    affiliation: Georgia Institute of Technology
    department: School of Industrial and Systems Engineering (ISyE)
    location: Atlanta, Georgia, USA
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence supporting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine the proportion of round wins immediately following a win streak. Given the round index, streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Finally, we find that sequences of round wins that are identified as non-random by the Wald-Wolfowitz run tests do not occur more or less frequently than expectated, further failing to provide evidence for the hot hand effect.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---

@@

[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/tonyelhabr/cod_snd/blob/master/data/cod_rounds.csv>.
